Setup Honeypot: Team Contagiarium

### 2011-11-01 Setup_honeypot.tex
Fixed reference errors

%A VPN session between the two hosts is possible, but might be considered as overkill and still does not garantee delivery.
We have decided to set up a reverse SSH tunnel from the monitoring machine to the honeypot machine, as described in the article ``Remote logging with syslog-ng''. \cite{Remote_logging}
The command establishes an SSH connection the honeypot, setting options to forego a login shell or anything a normal user would desire, and binds the local socket 9514 on the honeypot machine to tunnel its connections to the same port on our monitoring machine.
We have put this command there in a script to allow the connection to be re-esthablished quickly and easily if the SSH session is terminated for some reason.

We have configured a locally installed the \verb|syslog-ng| package for our \verb|util| account user, configured it to listen to local TCP connections on port 9514 and thereby receive syslog messages transmitted through this port.

@@

\subsection{scanlogd}
To detect port scans we have installed the service scanlogd.
Per detected scan an entry is written to syslog.

@@

\emph{iptables -I INPUT -m state --state NEW -j LOG --log-prefix "New Connection: "}
\emph{iptables -I OUTPUT -m state --state NEW -j LOG --log-prefix "New Connection: "}

>>>>

%A VPN session between the two hosts is possible, but might be considered as overkill and still does not garantee delivery.
We have decided to set up a reverse SSH tunnel from the monitoring machine to the honeypot machine, as described in the article ``Remote logging with SSH and syslog-ng''. \cite{remote_logging}
The example command establishes an SSH connection the honeypot, setting options to forego a login shell or anything a normal user would desire, and binds the local socket 9514 on the honeypot machine to tunnel its connections to the same port on our monitoring machine.
We have put this command in a script to allow the connection to be re-esthablished quickly and easily if the SSH session is terminated for some reason.

We have configured a locally installed the \verb|syslog-ng| package for our user on the monitoring machine, and configured it to listen to local TCP connections on port 9514 and thereby receive syslog messages transmitted through this port.

@@

\subsection{scanlogd}
To detect port scans we have installed the service \verb|scanlogd|.
Per detected scan an entry is written to syslog.

@@

\verb|iptables -I INPUT -m state --state NEW -j LOG --log-prefix "New Connection: "|
\verb|iptables -I OUTPUT -m state --state NEW -j LOG --log-prefix "New Connection: "|
